A diathesis is a sentence structure that reshapes the expression of the roles of a verb. This book presents an encyclopaedic survey of diathesis in German. Currently almost 250 different German diatheses are described in this book, some highly productive, some only attested for a handful of verbs. The main goal of this book is to present this wealth of grammatical possibility in a unified manner, while at the same time attempting to classify and organise this diversity. A summary of the about 80 most prominent diatheses is also provided, including many newly minted German names, because most of these diatheses did not have a German name yet.

Except for diathesis this book also aims to completely catalogue its counterpart: epithesis. An epithesis is a derived sentence structure in which the marking of the roles is not changed. Basically, these are the grammaticalised constructions expressing tense-aspect-mood-evidentiality in German. The list of major epitheses is also quite long (about 40 constructions), but it is quite a bit smaller than the list of major diatheses (about 80 constructions). This indicates that from a purely grammatical perspective, diathesis (`grammatical voice') is about a two-times more elaborate topic than epithesis (`tense-aspect-mood marking') in German.

\vspace{1\baselineskip}

\noindent\textbf{Michael Cysouw} is professor for language typology and quantitative linguistics at the Philipps-Universität Marburg. He is the author of \textit{The paradigmatic structure of person marking} and co-author of the \textit{Unicode cookbook for linguists}. His main research interest is the broad-scale investigation of the world's linguistic diversity, with a particular fondness for unusual structures from a worldwide perspective. This book represents a new avenue of his research, investigating a seemingly familiar language from a typologically inspired perspective.
